---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(nflscrapR)

week_3_games <- scrape_game_ids(2018, weeks= 3)

```{r}
week_3_games %>%
  pander::pander()
```

```{r}
library(tidyverse)
```


```{r}
lar_vs_lac_pbp <- week_3_games %>%
  filter(home_team == "LA") %>%
  pull(game_id) %>%
  scrape_json_play_by_play()

KC_vs_SF_pbp <- kcsf %>%
  filter(home_team == "KC") %>%
  pull(game_id) %>%
  scrape_json_play_by_play()
```

```{r}
library(teamcolors)
#Pull out the Rams and Chargers colors:
nfl_teamcolors <- teamcolors %>% filter(league == "nfl")
lar_color <- nfl_teamcolors %>%
  filter(name == "Los Angeles Rams") %>%
  pull(primary)
lac_color <- nfl_teamcolors %>%
  filter(name == "Los Angeles Chargers") %>%
  pull(tertiary)

#Pull out the Chiefs and 49ers colors:
nfl_teamcolors <- teamcolors %>% filter(league == "nfl")
kc_color <- nfl_teamcolors %>%
  filter(name == "Kansas City Chiefs") %>%
  pull(primary)
sf_color <- nfl_teamcolors %>%
  filter(name == "San Fransico 49ers") %>%
  pull(tertiary)

```

```{r}
# Now generate the win probability chart:
lar_vs_lac_pbp %>%
  filter(!is.na(home_wp),
         !is.na(away_wp)) %>%
  dplyr::select(game_seconds_remaining,
                home_wp,
                away_wp) %>%
  gather(team, wpa, -game_seconds_remaining) %>%
  ggplot(aes(x = game_seconds_remaining, y = wpa, color = team)) +
  geom_line(size = 1) +
  geom_hline(yintercept = 0.5, color = "gray", linetype = "dashed") +
  scale_color_manual(labels = c("LAC", "LAR"),
                     values = c(lac_color, lar_color),
                     guide = FALSE) +
  scale_x_reverse(breaks = seq(0, 3600, 300)) + 
  annotate("text", x = 3000, y = .75, label = "LAC", color = lac_color, size = 8) + 
  annotate("text", x = 3000, y = .25, label = "LAR", color = lar_color, size = 8) +
  geom_vline(xintercept = 900, linetype = "dashed", black) + 
  geom_vline(xintercept = 1800, linetype = "dashed", black) + 
  geom_vline(xintercept = 2700, linetype = "dashed", black) + 
  geom_vline(xintercept = 0, linetype = "dashed", black) + 
  labs(
    x = "Time Remaining (seconds)",
    y = "Win Probability",
    title = "Week 3 Win Probability Chart",
    subtitle = "Los Angeles Chargers vs. Los Angeles Rams",
    caption = "Data from nflscrapR"
  ) + theme_bw()
```

